Recent demography drives changes in linked selection across the maize genome

### 2015-12-06 PlosGen/manuscript.tex
plos

%\documentclass[twocolumn,twoside]{article}
\documentclass[twoside, twocolumn, letterpaper]{article}
\usepackage{graphics}
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\usepackage{NatGenArtT}
%\usepackage{NatureLetT}
\usepackage{times}
\DeclareMathAlphabet{\msfsl}{OT1}{cmss}{m}{sl}
\DeclareMathAlphabet{\msfrg}{OT1}{cmss}{n}{sl}
\renewcommand{\baselinestretch}{1}
\addtolength{\oddsidemargin}{-.2cm}
\addtolength{\evensidemargin}{-1.2cm}
\addtolength{\textwidth}{1.5cm}
\addtolength{\topmargin}{-1.75cm}
\addtolength{\textheight}{3.5cm}
\renewcommand{\textfraction}{0.01}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.65}
\renewcommand{\floatpagefraction}{0.90}
\renewcommand{\dbltopfraction}{0.95}
\renewcommand{\dblfloatpagefraction}{0.80}
\renewcommand{\sfdefault}{phv}

\usepackage[sort&compress]{natbib}
\bibpunct{}{}{,}{s}{}{\textsuperscript{,}}
\usepackage{amsmath}
\usepackage{graphicx}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\tablename}{Supplementary Table}%
        \setcounter{figure}{0}
        \renewcommand{\figurename}{Supplementary Figure}%
}

\makeatletter
\renewcommand{\footnotesep}{-2pt}
\makeatletter

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

% fancy for Nature Genetics
\fancyhead[RO]{\begin{picture}(600,1)(10,20)\put(440,32) {\textcolor{Dgreen}{\large{\sfbf{ANALYSIS}}}}\end{picture}}
\fancyhead[RE]{\begin{picture}(600,1)(10,20)\put(10,32)  {\textcolor{Dgreen}{\large{\sfbf{ANALYSIS}}}}\end{picture}}
\fancyhead[C]{\begin{picture}(600,1)(10,20)\linethickness{50pt}\put(-43,52) {{\color{pTop}{\line(1,0){615}}}}\linethickness{0.5pt}\put(10,-678) {{\line(1,0){515}}}\end{picture}}

\fancyfoot[RO]{\thepage}
\fancyfoot[LE]{\thepage}

\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{
    \fancyhf{}
}
\setcounter{footnote}{0}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Recent demography drives changes in linked selection across the maize genome}

\author{
  Timothy M. Beissinger\thanks{Dept. of Plant Sciences, University of California, Davis, CA, USA} $^,$\thanks{US Department of Agriculture, Agricultural Research Service, Columbia, MO, USA} $^,$\thanks{Division of Plant Sciences, University of Missouri, Columbia, MO, USA} $^{,6}$\hspace{.5mm},
  Li Wang\thanks{Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, IA, USA} \hspace{.5mm},
  Kate Crosby$^{1,}$ \hspace{.5mm},
  Arun Durvasula$^{1,}$ \hspace{.5mm},
  Matthew B. Hufford$^{4,}$ \hspace{.5mm},
  Jeffrey Ross-Ibarra$^{1,}$\thanks{Genome Center and Center for Population Biology, University of California, Davis, CA, USA} $^{,}$\thanks{Correspondence should be addressed to TMB (beissingert@missouri.edu) or JRI (rossibarra@ucdavis.edu).}
  }

\date{\small Manuscript intended for \emph{Nature Genetics}, \today}

\begin{document}
\maketitle

\begin{abstract}
  \noindent \bf
  \noindent
Genetic diversity is shaped by the interaction of drift and selection, but the details of this interaction are not well understood. Although a population's propensity to drift is typically summarized by its long-term effective population size ($N_e$ ), rapidly changing population demographics complicate this relationship. To better understand how changing demography impacts selection, we used whole-genome sequencing data to investigate patterns of linked selection in domesticated and wild maize (teosinte). We produce the first whole-genome estimate of the demography of maize domestication, showing that maize was reduced to approximately 5\% the population size of teosinte before it experienced rapid expansion post-domestication to population sizes much larger than its ancestor. Evaluation of patterns of nucleotide diversity in and near genes shows little evidence of selection on beneficial amino acid substitutions, and that the domestication bottleneck lead to a decline in the efficiency of purifying selection in maize.  Young alleles, however, show evidence of much stronger purifying selection in maize, reflecting the much larger effective size of present day populations. Our results demonstrate that recent demographic change --- a hallmark of many species including both humans and crops ---  can have immediate and wide-ranging impacts on diversity that conflict with would-be expectations based on $N_e$ alone.
\end{abstract}

@@

@@

@@

@@

\begin{figure}[!tb]
  \begin{center}
  \includegraphics[width=.45\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{\textbf{A} and \textbf{B} show mean pairwise diversity $\pi$, $\pm$ one standard deviation, while \textbf{C} and \textbf{D} depict and Tajimas D in 1kb windows from genic and nongenic regions of maize and teosinte.   \label{fig:diversity} }
\end{figure}

\begin{figure}[!tb]
%\vspace*{.05in}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/DomesticationModel/domesticationModel.pdf}
\caption{Parameter estimates for a basic bottleneck model of maize domestication. See methods for details. \label{fig:bottleneck} }
\end{figure}

@@

%\mbh{I'm curious whether linked selection is affecting the diversity around a sizable proportion of synonymous substitutions.  Would it be worthwhile to look at diversity around the subset of synonymous substitutions that are the least linked to missense substitutions just to make sure it is not substantially higher? Or perhaps generate a plot of diversity around synonymous substitutions vs. distance of these subs from missense subs?}

\begin{figure*}[tb]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_Aug}
\hspace{0.05\textwidth} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_Significance_Aug}
\caption{Pairwise diversity surrounding synonymous and missense  substitutions in {\bf A} maize and {\bf B} teosinte. Axes show absolute diversity values (right) and values relative to mean nucleotide diversity in windows $\geq 0.01 cM$ from a substitution (left).  Lines depict a loess curve (span of 0.01) and shading represents bootstrap-based 95\% confidence intervals. Inset plots depict a larger range on the x-axis. \label{fig:hardSweeps}}
\end{figure*}

@@

@@

\begin{figure*}[!tb]
%\vspace*{.05in}
\centering
\includegraphics[width=.45\textwidth]{FigsAndFiles/distanceToGene_WithSignificance_Folded2_manuscript.png} \includegraphics[width=.45\textwidth]{FigsAndFiles/distanceToGene_WithSignificance_Singletons_Downsampled_threeLines_manuscript.png}
\caption{Relative diversity versus distance to nearest gene in maize and teosinte. 
Shown are \textbf{A} pairwise nucleotide diversity and \textbf{B} singleton diversity.  
Relative diversity is calculated compared to the mean diversity in windows $\geq 0.01 cM$ or $\geq 0.02 cM$ from the nearest
gene for pairwise diversity and singletons, respectively. 
  Lines depict cubic smoothing splines with smoothing parameters chosen via generalized cross validation and shading depicts bootstrap-based 95\% confidence intervals.
  Inset plots depict a smaller range on the x-axis. \label{fig:purify}
  }
\end{figure*}

@@

\section*{DISCUSSION}

%\subsection*{Demography of domestication} %JRI
Although a number of authors have investigated the demography of maize domestication \cite{eyre1998, tenaillon2004, wright2005}, these  efforts relied on data only from genic regions of the genome and made a number of limiting assumptions about the demographic model.  We show that diversity within genes has been strongly reduced by the effects of linked selection, such that even synonymous polymorphisms in genes are not representative of diversity at unconstrained sites. This implies that genic polymorphism data are unable to tell the complete or accurate demographic history of maize, but the rapid recovery of diversity outside of genes demonstrates that sites far from genes can be reasonably used for demographic inference. Furthermore, by utilizing the full joint SFS, we are able to estimate population growth, gene flow, and the strength of the domestication bottleneck without making assumptions about its duration.

@@

%\subsection*{Hard sweeps do not shape genome-wide diversity in maize} %JRI

@@

%\subsection*{Demography influences the efficiency of purifying selection} %JRI 
One of our more striking findings is that the impact of purifying selection on maize and teosinte qualitatively changed over time. 
We observe a more pronounced decrease in $\pi$ around genes in teosinte than maize (Figure \ref{fig:purify}A), but the opposite trend when we evaluate diversity using singleton polymorphisms (Figure \ref{fig:purify}B).
The efficiency of purifying selection is proportional to effective population size \cite{kimura1984}, and these results are thus consistent with our demographic analyses which show a domestication bottleneck and smaller long-term $N_e$ in maize \cite{eyre1998, tenaillon2004, wright2005, ross2009} followed by recent rapid expansion and a much larger modern $N_e$.

@@

%\section*{Rapid changes in linked selection} %JRI
Most importantly, our results demonstrate that consideration of long-term differences in $N_e$ cannot fully capture the dynamic relationship between demography and selection. 
While a number of authors have tested for selection using methods that explicitly incorporate or are robust to demographic change \cite{eyre2009estimating, chen2010, zeng2010} and others have compared estimates of the efficiency of adaptive and purifying selection across species \cite{popadin2012} or populations \cite{Elyashiv:2010ga}, previous analyses of the impact of linked selection on genome-wide diversity have relied on single estimates of the effective population size \cite{corbett2015,leffler2012}.
Our results show that demographic change over short periods of time can quickly change the dynamics of linked selection: mutations arising in extant maize populations are much more strongly impacted by the effects of selection on linked sites than would be suggested by analyses using long-term effective population size.
As many natural and domesticated populations have undergone considerable demographic change in their recent past, long-term comparisons of $N_e$ are likely not informative about current processes affecting allele frequency trajectories.

\section*{METHODS}
Methods and any associated references are available in a separate pdf file.

\section*{ACKNOWLEDGEMENTS}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.

\section*{AUTHOR CONTRIBUTIONS}
TMB and JRI devised this study. TMB, LW, and KC analyzed the data. AD performed early-stage simulations. MBH provided advice. TMB, JRI, and MBH wrote the manuscript.

\section*{COMPETING INTERESTS STATEMENT}
The authors declare no competing financial interests.

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{naturemag}
%\bibliographystyle{NatureSeriesT}
\bibliography{Reference}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section*{ONLINE METHODS}
\subsection*{BASH, R, and Python scripts}
All scripts used for analysis are available in an online repository at \url{https://github.com/timbeissinger/Maize-Teo-Scripts}.

@@

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (http://lh3lh3.users.sourceforge.net/snpable.shtml). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameters $20\times2+20\times4+10\times2$.

@@

\onecolumn
\input{supportingInfo}

>>>>

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Recent demography drives changes in linked selection across the maize genome}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Timothy M. Beissinger\textsuperscript{1,2,3,*},
Li Wang\textsuperscript{4},
Kate Crosby\textsuperscript{1},
Arun Durvasula\textsuperscript{1},
Matthew B. Hufford\textsuperscript{4},
Jeffrey Ross-Ibarra\textsuperscript{1,5,*},
\\
\bigskip
\bf{1} Department of Plant Sciences, University of California, Davis, Caliornia, USA\\
\bf{2} US Department of Agriculture, Agriculture Research Service, Columbia, Missouri, USA\\
\bf{3} Division of Plant Sciences, University of Missouri, Columbia, Missouri, USA\\
\bf{4} Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, Iowa, USA\\
\bf{5} Genome Center and Center for Population Biology, University of California, Davis, California, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
%\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* rossibarra@ucdavis.edu or beissingert@missouri.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Genetic diversity is shaped by the interaction of drift and selection, but the details of this interaction are not well understood. Although a population's propensity to drift is typically summarized by its long-term effective population size ($N_e$ ), rapidly changing population demographics complicate this relationship. To better understand how changing demography impacts selection, we used whole-genome sequencing data to investigate patterns of linked selection in domesticated and wild maize (teosinte). We show that maize went through a domestication bottleneck with a population size of approximately 5\% that of teosinte before it experienced rapid expansion post-domestication.  We observe that hard sweeps on genic mutations are not the primary force driving maize evolution. As expected, a reduced population size during domestication decreased the efficiency of purifying selection to purge deleterious alleles from maize, but rapid expansion after domestication has since increased the efficiency of purifying selection to levels exceeding those seen in teosinte. This final observation demonstrates that rapid demographic change can have wide-ranging impacts on diversity that conflict with would-be expectations based on long-term $N_e$.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
Both selection and demographic change play important roles in shaping genetic diversity, but there are few empirical examples of the interplay between them. Although it is well known that both diversity and the efficacy of natural selection are reduced in smaller populations, the short-term consequences of demographic change on linked selection have not been well studied. We use wild and domesticated maize to demonstrate that rapid changes in population size impact the effect of selection on linked sites in ways not well described by long-term average population size. We also produce an unbiased estimate of maize demographic history and show that positive selection on new genic mutations plays a lesser role in shaping diversity than purifying selection against deleterious mutations.

\linenumbers

\section*{Introduction}

@@

% Results and Discussion can be combined.

@@

\begin{figure}[h]
%  \begin{center}
%  \includegraphics[width=.45\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
%\end{center}
\caption{{\bf Diversity and Tajima's D in maize and teosinte.} \textbf{A} and \textbf{B} show mean pairwise diversity $\pi$, $\pm$ one standard deviation, while \textbf{C} and \textbf{D} depict and Tajimas D in 1kb windows from genic and nongenic regions of maize and teosinte.   \label{fig:diversity} }
\end{figure}

@@

\begin{figure}[h]
%\vspace*{.05in}
%\centering
%\includegraphics[width=.5\textwidth]{FigsAndFiles/DomesticationModel/domesticationModel.pdf}
\caption{{\bf Parameter estimates for a basic bottleneck model of maize domestication.} See methods for details. \label{fig:bottleneck} }
\end{figure}

@@

@@

\begin{figure*}[h]
%\vspace*{.05in}
%\centering
%\includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_Aug}
%\hspace{0.05\textwidth} \includegraphics[width=.45\textwidth]{FigsAndFiles/plotDiversity_TvT_Folded2_Significance_Aug}
\caption{ {\bf Pairwise diversity surrounding synonymous and missense  substitutions in {\bf A:} maize and {\bf B:} teosinte.} Axes show absolute diversity values (right) and values relative to mean nucleotide diversity in windows $\geq 0.01 cM$ from a substitution (left).  Lines depict a loess curve (span of 0.01) and shading represents bootstrap-based 95\% confidence intervals. Inset plots depict a larger range on the x-axis. \label{fig:hardSweeps}}
\end{figure*}

@@

\begin{figure*}[h]
%\vspace*{.05in}
%\centering
%\includegraphics[width=.45\textwidth]{FigsAndFiles/distanceToGene_WithSignificance_Folded2_manuscript.png} \includegraphics[width=.45\textwidth]{FigsAndFiles/distanceToGene_WithSignificance_Singletons_Downsampled_threeLines_manuscript.png}
\caption{ {\bf Relative diversity versus distance to nearest gene in maize and teosinte.} 
Shown are \textbf{A} pairwise nucleotide diversity and \textbf{B} singleton diversity.  
Relative diversity is calculated compared to the mean diversity in windows $\geq 0.01 cM$ or $\geq 0.02 cM$ from the nearest
gene for pairwise diversity and singletons, respectively. 
  Lines depict cubic smoothing splines with smoothing parameters chosen via generalized cross validation and shading depicts bootstrap-based 95\% confidence intervals.
  Inset plots depict a smaller range on the x-axis. \label{fig:purify}
  }
\end{figure*}

@@

@@

\section*{Discussion}

\subsection*{Demography of domestication} %JRI
Although a number of authors have investigated the demography of maize domestication \cite{eyre1998, tenaillon2004, wright2005}, these  efforts relied on data only from genic regions of the genome and made a number of limiting assumptions about the demographic model.  We show that diversity within genes has been strongly reduced by the effects of linked selection, such that even synonymous polymorphisms in genes are not representative of diversity at unconstrained sites. This implies that genic polymorphism data are unable to tell the complete or accurate demographic history of maize, but the rapid recovery of diversity outside of genes demonstrates that sites far from genes can be reasonably used for demographic inference. Furthermore, by utilizing the full joint SFS, we are able to estimate population growth, gene flow, and the strength of the domestication bottleneck without making assumptions about its duration.

@@

\subsection*{Hard sweeps do not shape genome-wide diversity in maize} %JRI

@@

\subsection*{Demography influences the efficiency of purifying selection} %JRI 
One of our more striking findings is that the impact of purifying selection on maize and teosinte qualitatively changed over time. 
We observe a more pronounced decrease in $\pi$ around genes in teosinte than maize (Figure \ref{fig:purify}A), but the opposite trend when we evaluate diversity using singleton polymorphisms (Figure \ref{fig:purify}B).
The efficiency of purifying selection is proportional to effective population size \cite{kimura1984}, and these results are thus consistent with our demographic analyses which show a domestication bottleneck and smaller long-term $N_e$ in maize \cite{eyre1998, tenaillon2004, wright2005, ross2009} followed by recent rapid expansion and a much larger modern $N_e$.

@@

\section*{Rapid changes in linked selection} %JRI
Our results demonstrate that consideration of long-term differences in $N_e$ cannot fully capture the dynamic relationship between demography and selection. 
While a number of authors have tested for selection using methods that explicitly incorporate or are robust to demographic change \cite{eyre2009estimating, chen2010, zeng2010} and others have compared estimates of the efficiency of adaptive and purifying selection across species \cite{popadin2012} or populations \cite{Elyashiv:2010ga}, previous analyses of the impact of linked selection on genome-wide diversity have relied on single estimates of the effective population size \cite{corbett2015,leffler2012}.
Our results show that demographic change over short periods of time can quickly change the dynamics of linked selection: mutations arising in extant maize populations are much more strongly impacted by the effects of selection on linked sites than would be suggested by analyses using long-term effective population size.
As many natural and domesticated populations have undergone considerable demographic change in their recent past, long-term comparisons of $N_e$ are likely not informative about current processes affecting allele frequency trajectories.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

\subsection*{BASH, R, and Python scripts}
All scripts used for analysis are available in an online repository at \url{https://github.com/timbeissinger/Maize-Teo-Scripts}.

@@

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (\url{http://lh3lh3.users.sourceforge.net/snpable.shtml}). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameters $20\times2+20\times4+10\times2$.

@@

\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
\input{supportingInfo}

\section*{Acknowledgments}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%

\bibliography{Reference}
